---
title: "BEATcc_MO39872_KN826_PoS"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: "Anh Nguyen Duc"
output:
  html_document:
    toc: yes
    toc_float: true
    to_depth: 5
    collapsed: false
    smooth_scroll: false
    number_sections: true
    theme: united
  word_document: default
header-includes: \usepackage{docmute}
classoption: landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(knitr)
require(rpact)# for group sequential design
require(gMCP) # for multiple testing
require(MASS) # for simulation from multivariate normal dist.
require(mvtnorm) # for pmvnorm
# require(bpp)
require(haven)
require(survival)
require(meta)
require(bayesmeta)
require(metafor)
# source("https://raw.github.roche.com/adaptR/adaptR-tutorials/master/simpleBoundarySummary.R")
```


## Supportive techinical resource

+ https://arxiv.org/pdf/1711.08683.pdf 

+ (https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1217 

## Approach

+ Use random fixed effect model to meta-analyze outcomes from IMagyn050 and KN826 and then consider the reulting posterior predictive distribution for BEATcc to predict its POS at the IA (https://arxiv.org/pdf/1711.08683.pdf). Specifically,

    + Prior distribution for effect (log HR) parameter: (improper) uniform prior is used.
    
    + Prior distribution for $\tau$ (heterogeneity / across studies variance) parameter: weakly informative half-normal prior with scale of 0.5 to cover a wide range of cross-study heterogeneity (https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1217).

+ As one is not clear about the observed benefit from KN826, the PoS based on various assumed observed HR for PFS is considered.

+ Intrinsic colleration between PFS and OS from BEATcc as well as the potential for $\alpha$-recycling are ignored. Hence results could likely serve as lower boundary for PoS.

## Assumption

+ Merck considered a hierarchy of: CPS$\ge$10 PFS $\rightarrow$ ITT PFS $\rightarrow$ CPS$\ge$10 OS $\rightarrow$ ITT OS i.e. with this the announcement means all endpoints were tested at full alpha of 5%.

+ Prevalence of CPS$\ge$10 = 70%, hence the observed number of PFS events for ITT was $227/0.7$ and OS-ITT events of $184/0.7$.

## PoS for PFS

### At the efficacy boundary from KN826 for PFS

```{r, echo=TRUE, warning=TRUE, results='asis'}
## PFS

# get the efficacy boundary for KN826
deg_PFS_826 <- getDesignGroupSequential(kMax = 2, alpha = 0.025, sided = 1, informationRates = c(182, 227)/227)

# HR PFS ITT = 0.73 is based on trial-errors to get 260 and 324 PFS events at 1st and 2nd IA (PFS FA)
sam_PFS_826 <- getSampleSizeSurvival(design = deg_PFS_826, hazardRatio = 0.73)
sam_PFS_826 %>% summary

meta_PFS <- bayesmeta(y      = c(log(0.92),              log(sam_PFS_826$criticalValuesEffectScale[2])), 
                      sigma  = c(2/sqrt(664),            2/sqrt(227/.7) ),
                      labels = c('IMagyn050 Pimary CSR', "KN826"),
                      tau.prior = function(x){dhalfnormal(x,scale=1)})

meta_PFS %>% print
forestplot(meta_PFS) %>% print

# This follows p27 of "Bayesian Random-Effects Meta-Analysis Using the bayesmeta R Package"
foo <- function(x) meta_PFS$dposterior(mu = x, predict = TRUE) * pnorm( (0.756%>%log - x) / (2/sqrt(280))  )

integrate(foo, lower=-Inf, upper=Inf)$value # Please note we need to use this for the effect estimate not the "true" study effect size

```

### At several assumed observed PFS HR ITT from KN826
```{r, echo=TRUE, warning=TRUE, results='asis'}
# now we run through several assumed observed HR for PFS from KN826
# hrPFS_826 <- c(0.7986178, seq(.79, .7, -.005))

hrPFS_826 <- c(0.7986178, .775, .750, .725, .7, .675, .65)

PoS_PFS   <- Pos_PFS_no_050<- NULL

for (hr_pfs in hrPFS_826) {
  meta_pfs <- bayesmeta(y      = c(log(0.92),              log(hr_pfs)), 
                        sigma  = c(2/sqrt(664),            2/sqrt(227/.7) ),
                        labels = c('IMagyn050 Pimary CSR', "KN826"),
                        tau.prior = function(x){dhalfnormal(x,scale=1)})

  foo <- function(x) meta_pfs$dposterior(mu = x, predict = TRUE) * pnorm( (0.756%>%log - x) / (2/sqrt(280))  )

  PoS_PFS        <- c(PoS_PFS, integrate(foo, lower=-Inf, upper=Inf)$value )
  Pos_PFS_no_050 <- c(Pos_PFS_no_050, pnorm( (0.756%>%log - hr_pfs%>%log) / (2/sqrt(280))  ) )
} # end of for (hr_pfs %in% hrPFS_826)

# plot(hrPFS_826, PoS_PFS, type='l', bty="7", xlab='Observed PFS HR in ITT in KN826', ylab='PoS for PFS in BEATcc')
rbind('hrPFS_826'=hrPFS_826, 'PoS_PFS_BEATcc'=PoS_PFS, 'PoS_PFS_BEATcc_no_050'=Pos_PFS_no_050) %>% kable(digits = 3, col.names = rep('.', PoS_PFS %>% length), row.names = T) %>% print
```

## PoS for OS (IA)

### At several assumed observed OS HR ITT from KN826
```{r, echo=TRUE, warning=TRUE, results='asis'}
# now we run through several assumed observed HR for PFS from KN826
# hrOS_826 <- c(0.82, seq(.79, .7, -.005))
hrOS_826 <- c(0.82, .8, .75, .7)

PoS_OS   <- Pos_OS_no_050 <- NULL

for (hr_OS in hrOS_826) {
  meta_OS <- bayesmeta(y      = c(log(0.96),              log(hr_OS)), 
                       sigma  = c(2/sqrt(219),            2/sqrt(184/.7) ),
                       labels = c('IMagyn050 Pimary CSR', "KN826"),
                       tau.prior = function(x){dhalfnormal(x,scale=1)})

  foo <- function(x) meta_OS$dposterior(mu = x, predict = TRUE) * pnorm( (0.68%>%log - x) / (2/sqrt(197))  )
  
  PoS_OS        <- c(PoS_OS, integrate(foo, lower=-Inf, upper=Inf)$value )
  Pos_OS_no_050 <- c(Pos_OS_no_050, pnorm( (0.68%>%log - hr_OS%>%log) / (2/sqrt(197))  ) )  
} # end of for (hr_OS %in% hrOS_826)

# plot(hrOS_826, PoS_OS, type='l', bty="7", xlab='Observed OS HR in ITT in KN826', ylab='PoS for OS in BEATcc')
rbind('hrOS_826'=hrOS_826, 'PoS_OS_BEATcc'=PoS_OS, 'PoS_OS_BEATcc_no_050'=Pos_OS_no_050) %>% kable(digits = 3, col.names = rep('.', PoS_OS %>% length), row.names = T) %>% print
```